\vspace{-1em}Guidance, please! Towards a framework for RDF-based constraint languages.

### 2015-07-16 paper/paper 2/dc-2015.tex
minor

\begin{ex}[commandchars=\\\{\}]
Publication 
    a owl:Restriction ;
    owl:minQualifiedCardinality 1 ;
    owl:onProperty author ;
    owl:onClass Person .
\end{ex}

@@

SPIN is used to execute the mapping, the property \emph{spin:rule} links an rdfs:Class with SPARQL CONSTRUCT queries. Each query defines an inference rule that is applied to all instances of the associated class and its subclasses. The inference rule defines how additional triples can be inferred from what is stated in the WHERE clause. For each binding of the pattern in the WHERE clause of the rule, the triple templates from the CONSTRUCT clause are instantiated and added as inferred triples to the underlying model. At query execution time, the SPARQL variable ?this is bound to the current instance of the class. As each resource per default is assigned to the class owl:Thing, this inference rule is evaluated for each subject of the input RDF graph.

@@

As stated in Section~\ref{sec:motivation}, we see a huge potential in the possibility to transform semantically equivalent constraints from one high level constraint language to another via the RDF-CV representation, to avoid that every possible combination of constraint languages has to be mapped separately. The following SPIN inference rule exemplifies this approach and provides a mapping from RDF-CV back to an OWL2 constraint:

>>>>

\begin{ex}[commandchars=\\\{\}]
:Publication 
    a owl:Restriction ;
    owl:minQualifiedCardinality 1 ;
    owl:onProperty :author ;
    owl:onClass :Person .
\end{ex}

@@

SPIN is used to execute the mapping, the property \emph{spin:rule} links an rdfs:Class with SPARQL CONSTRUCT queries. Each query defines an inference rule that is applied to all instances of the associated class and its subclasses. The inference rule defines how additional triples can be inferred from what is stated in the WHERE clause. For each binding of the pattern in the WHERE clause of the rule, the triple templates from the CONSTRUCT clause are instantiated and added as inferred triples to the underlying model. At query execution time, the SPARQL variable \emph{?this} is bound to the current instance of the class. As each resource per default is assigned to the class \emph{owl:Thing}, this inference rule is evaluated for each subject of the input RDF graph.

@@

As stated in Section~\ref{sec:motivation}, we see a huge potential in the possibility to transform semantically equivalent constraints from one high-level constraint language to another via the RDF-CV representation, to avoid that every possible combination of constraint languages has to be mapped separately. The following SPIN inference rule exemplifies this approach and provides a mapping from RDF-CV back to an OWL2 constraint:
